Developing effective theories for single and bilayer graphene using density matrix downfolding

### 2019-09-11 reoutline.tex
finished preliminary work. need to make bib shorter...
updated reoutline

\section{Fixed-node diffusion Monte Carlo (FN-DMC)}
\begin{enumerate}
\item Diffusion Monte Carlo (DMC) is a quantum Monte Carlo method which projects out the ground state of a real-space Hamiltonian given some initial trial wave function.
%Talk about efficiency here

\item DMC, however, suffers from a fermion sign problem which is alleviated via a fixed-node approximation.
%Talk about accuracy here, compare to other methods

@@

\item The training data required for downfolding are extracted from the projected low-energy states via a mixed estimator.
%Start paragraph with something else, probably the stochastic representation of the wave function
\end{enumerate}

@@

%sampling low energy states
\item Explain why MSJ was chosen (Probably the hardest one)

\item How determinants selected

\item How coefficients selected

\item How Jastrow optimized and FN-DMC done

@@

@@

%Solutions of the model 
\item The model is solved by exact diagonalization, and the solutions agree well with experimental spectra and state assignments.

\item The model states also agree with recent theoretical calculations like UKS and CCSD(T).

\end{enumerate}

>>>>

\section{Fixed-node diffusion Monte Carlo (FN-DMC)}
\begin{enumerate}
\item Diffusion Monte Carlo (DMC) is a quantum Monte Carlo method which projects out the ground state of a real-space Hamiltonian given some initial trial wave function.

\item DMC, however, suffers from a fermion sign problem which is alleviated via a fixed-node approximation.

@@

\item The training data required for downfolding are extracted from the projected low-energy states via a mixed estimator.
\end{enumerate}

@@

%Sampling LE states
\item For the CuO molecule, low-energy states were generated by using FN-DMC projected multi-Slater-Jastrow (MSJ) trial wave functions.

\item The determinants $|D_j \rangle$ were constructed from the orbitals of independent symmetry-targeted unrestricted Kohn Sham (UKS) calculations.

\item A shell sampling scheme was used to sample states from the selected approximate low-energy space.

@@

\item A single three-body Jastrow factor was used for all trial wave functions, and was optimized on the lowest energy determinant $|D_0 \rangle$ using an energy optimization scheme \cite{Toulouse2007}.

@@

%Solutions of the model 
\item The model was solved by exact diagonalization, and the solutions agree well with experimental spectra and state assignments.

\item The model states also agree with recent theoretical calculations like UKS and CCSD(T).
\end{enumerate}
